### 2022-07-06 introduction/introduction.tex
more

Though the interest for rigorous and formal reasoning dates back to Aristotle,
it intensified at the end of 19th and the beginning of 20th century
\cite{jf-01-modern-logic}. Researchers in that time were mostly interested in
finding a formal language that is expressive enough to describe many
mathematical theories, yet intuitive and understandable enough to allow
reasonably simple formal reasoning systems. Arguably, first-order logic seemed to satisfy
both requirements.  This formalism not only allows one to model simple logical
relations such as ``if it rains, the road is muddy'' (or formally $\cst{rains}
\iimplies \cst{muddy}$), but also to quantify over objects as in ``all people
are mortal'' ($\iforall x.\, \cst{human}(x) \iimplies \cst{mortal}(x)$).

@@

Integrating proof automation directly into the proof assistant is not an easy task.
Most proof assistants are based on variants of higher-order logic, which is more
expressive than first-order logic, but harder to automate as in general it does not even allow complete
proof calculi. To provide some level of automation, proof assistant developers
use the efficient first-order provers as follows. First, the proof goal is
translated from higher-order to first-order logic. Then the first-order prover
is run on the translated problem. If the first-order prover finds the proof, the
proof is reconstructed in the proof assistant. Modern assistants such as Coq \cite{bc-04-coq}, HOL Light \cite{jh-09-hol-light},
and Isabelle \cite{lc-88-isabelle} implement the approach using the \emph{hammers} CoqHammer
\cite{ck-18-coqhammer}, HOL(y)Hammer \cite{ku-15-holyhammer}, and Sledgehammer
\cite{bn-10-sh}, respectively.

>>>>

Though the interest for rigorous and formal reasoning dates back to Aristotle,
it intensified at the end of 19th and the beginning of 20th century
\cite{jf-01-modern-logic}. Researchers in that time were mostly interested in
finding a formal language that is expressive enough to describe many
mathematical theories, yet intuitive and understandable enough to allow
reasonably simple formal reasoning. First-order logic became a commonly used system that satisfies
both requirements.  This formalism not only allows one to model simple logical
relations such as ``if it rains, the road is muddy'' (or formally $\cst{rains}
\iimplies \cst{muddy}$), but also to quantify over objects as in ``all people
are mortal'' ($\iforall x.\, \cst{human}(x) \iimplies \cst{mortal}(x)$).

@@

Integrating proof automation directly into the proof assistant is not an easy task.
Most proof assistants are based on variants of higher-order logic, a logic expressive enough to
describe complex mathematical theories
out of reach for first-order logic.  However, it is harder to automate as in general it does not even allow complete
proof calculi. To provide some level of automation, proof assistant developers
use the efficient first-order provers as follows. First, the proof goal is
translated from higher-order to first-order logic. Then the first-order prover
is run on the translated problem. If the first-order prover finds the proof, the
proof is reconstructed in the proof assistant. Modern assistants such as Coq \cite{bc-04-coq}, HOL Light \cite{jh-09-hol-light},
and Isabelle \cite{lc-88-isabelle} implement the approach using the \emph{hammers} CoqHammer
\cite{ck-18-coqhammer}, HOL(y)Hammer \cite{ku-15-holyhammer}, and Sledgehammer
\cite{bn-10-sh}, respectively.
